### 2018-07-31 README.Rmd
even more reorganisation

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})")
  ) %>% 
  select(name, title) %>%
  knitr::kable()

@@

Explanation coming soon. Feel free to make an issue if you want your method to be included.

>>>>

scripts %>% filter(
  level == 1
) %>%
  arrange(ix) %>%
  mutate(
    name = str_glue("[{id}](https://github.com/dynverse/dynbenchmark/tree/master/{location})"),
    order = ifelse(is.na(ix), "", ix)
  ) %>% 
  select(order, subfolder = name, description = title) %>%
  knitr::kable()

@@

Explanation coming soon. Feel free to make an issue or send us an e-mail if you want your method to be included.
